%-------------------------
% Resume in LaTeX
% Author: BikalKumar Jha
% Website: https://github.com/jhabikal21/resume-ats
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% CV STARTS HERE

\begin{document}

% Heading
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://sourabhbajaj.com/}{\Large BikalKumar Jha}} & Email : \href{mailto:jha.bikal@yahoo.in}{jha.bikal@yahoo.in}\\
  \href{https://www.linkedin.com/in/devops-bikaljha/}{https://www.linkedin.com/in/devops-bikaljha/} & Mobile : +91-9722916319 \\
\end{tabular*}

% Summary
\section{Summary}
\begin{itemize}[leftmargin=*]
    \item Results-driven DevSecOps engineer with over 9 years of experience.
    \item Proven leadership capabilities as a technical team lead, fostering collaboration within cross-functional teams.
    \item Expertise in designing, implementing, and securing cloud-based infrastructure, deploying and managing security tools, conducting vulnerability assessments, identity and access management, and ensuring compliance with industry standards.
\end{itemize}


% Education
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Institute of Technology and Management (ITM) Universe}{Vadodara, India}
    {Bachelor of Engineering in Electronics Communication}{June. 2011 -- July. 2015}
\resumeSubHeadingListEnd

% Experience
\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {Resideo Smart Home Technologies}{Bangalore, IND}
    {Sr Advanced Tech Lead DevSecOps}{August 2025 - Present}
    \resumeItemListStart
      \resumeItem{Technical Leadership}
        {Provide technical leadership and strategic direction to embed security across the complete SDLC and CI/CD ecosystem, ensuring scalable, automated, and developer-friendly security practices.}
      \resumeItem{Enterprise DevSecOps Adoption}
        {Drive enterprise-wide adoption of DevSecOps by partnering with cross-functional engineering, platform, cloud, and product teams, enabling secure design, build, deployment, and operations.}
      \resumeItem{Security Architecture \& Risk Assessment}
        {Lead secure architecture reviews, threat modeling, and security risk assessments, translating findings into prioritized remediation strategies and long-term cyber risk reduction roadmaps.}
      \resumeItem{Security Standards \& Governance}
        {Define and institutionalize security standards, guardrails, policies, and best practices to proactively identify and mitigate vulnerabilities across applications, open-source components, and cloud-native platforms.}
      \resumeItem{Runtime Security \& Workload Protection}
        {Champion runtime security and workload protection, enabling detection of anomalous behavior, CVE exploit attempts, and threat alerts in production workloads.}
      \resumeItem{Kubernetes \& Cloud Security Hardening}
        {Oversee Kubernetes and cloud security hardening initiatives based on CIS benchmarks, enhancing baseline security posture and reducing attack surface for containerized workloads.}
      \resumeItem{Engineering Mentorship}
        {Mentor and guide engineers on secure coding, threat mitigation, and security tooling, building a continuous security-first mindset across engineering teams.}
      \resumeItem{Cross-functional Collaboration}
        {Act as the bridge between security leadership and engineering teams, ensuring transparency, measurable KPIs, and successful rollout of security capabilities at scale.}
    \resumeItemListEnd

    \resumeSubheading
    {Resideo Smart Home Technologies}{Bangalore, IND}
    {Technical Lead - DevSecOps}{April 2022 - Present}
    \resumeItemListStart
      \resumeItem{Leadership}
        {Lead the DevSecOps Automation Enablement team to facilitate the adoption of standard development toolsets and architecture patterns for onboarding applications onto the cloud.}
      \resumeItem{Product Security Reviews}
        {Conduct deep-dive analysis and maturity assessments of current DevOps practices, identifying and defining Automation Architecture Principles for building and enhancing automation frameworks and artifacts. Provide technical expertise to resolve automation engineering, coding, and architecture issues, supporting delivery projects throughout the project lifecycle.}
      \resumeItem{Automation}
        {Develop automation solutions for Cloud (Infrastructure as Code - Terraform), CI/CD pipelines (YAML), and QE processes for application technologies.}
    \resumeItemListEnd

    \resumeSubheading
    {Resideo Smart Home Technologies}{Bangalore, IND}
    {Senior Security Engineer - DevSecOps}{May 2020 - Apr 2022}
      \resumeItemListStart
        \resumeItem{Collaboration}
          {Interface with Cloud Engineering/Ops and DevTools teams on DevSecOps Automation-related issues, participating in the selection of automation tools and contributing to proof-of-concept implementations.
          Create educational materials and conduct training sessions on DevSecOps-related subjects, staying informed about industry trends and incorporating them into resources for development teams.
          Collaborate with cross-functional teams to integrate security into the build and deployment lifecycle.}
        \resumeItem{Shift Left Approach}
          {Implemented security best practices using agile methodology, led a team in implementing security practices using Hashicorp Sentinel for infrastructure deployment, integrated Prisma Cloud Compute with PingFederate, managed end-to-end vulnerabilities management, ensured microservices and applications are secure from vulnerabilities.}
        \resumeItem{SOC2 Audit}
          {Implement tooling needed for SOC2 audits (AWS GuardDuty, AWS Inspector, VPC Flow logs, AWS Detective, Cloudtrail, Splunk).}
        \resumeItem{Hashicorp Vault}
          {Integrated Hashicorp Vault with Azure AD using OIDC protocol, managed AD groups and policies in Vault for resource access across teams.}
        \resumeItem{Vulnerabilities Management}
          {Managed and implemented end-to-end vulnerabilities management tools like Tenable, CrowdStrike, and SentinelOne. Collaborated with teams for timely rectification and resolution of vulnerabilities.}
        \resumeItem{Containerized Echo-system}
          {Ensured security of microservices running on containerized echo-system or using orchestration tools like Kubernetes or OpenShift.}
        \resumeItem{CICD Implementation}
          {Integrated and managed CID implementation using Twistcli, published dashboard results, pushed teams for vulnerabilities fixes, and created governance rules.}
        \resumeItem{Operational Streamlining}
          {Implemented ad-hoc tools for operational streamlining using Akv2k8s, Sops (from Mozilla), Kube-hunter (in POC), etc.}
        \resumeItem{Firewall Model}
          {Implemented hub \& spoke firewall model and worked on operational issues related to central firewall (Fortinet Firewall/VPN, DR strategy).}
      \resumeItemListEnd

  \resumeSubheading
    {Qube Cinema Technology Pvt. Ltd}{Chennai, IND}
    {Software Engineer II - DevOps}{November 2018 -- May 2020}
    \resumeItemListStart
      \resumeItem{Build and Deployment Automation}
        {Configured Jenkins for build and deployment automation of various projects, worked on AWS ECS Cluster Node, and automated instance launching using Jenkins.}
      \resumeItem{DR-Performance}
        {Working on IaaC using Terraform for DR on the flagship product "QubeWire" which is an integrated solution for Movie producer and distributors. Adopting opensource solutions like iperf2, Alrta.io, Elastic APM, etc }
      \resumeItem{Migration}
        {Working on migrating cloud PostgreSQL to Aurora Serverless PostgreSQL. Migrating services and Application from on-prem datacenter to AWS. Deployed and monitored AWS infrastructure using Chef and Terraform, and defined projects and plans for the build and deployment process.}
    \resumeItemListEnd

  \resumeSubheading
    {Akamai Technologies}{Bangalore, IND}
    {Tech-Solution Engineer (DevOps)}{April 2017 -- November 2018}
    \resumeItemListStart
      \resumeItem{Deployment Automation}
        {Responsible for deployment automation using tools like Chef, Jenkins, Git, and Ant scripts.}
      \resumeItem{Real-Time Monitoring}
        {Work on real-time customer traffic monitoring, actively participate in troubleshooting, and contribute to the migration of streams and provisioning/un-provisioning processes during maintenance.}
      \resumeItem{Operations}
        {Participate actively in the internal development team, building and deploying applications, migrating services and applications between clouds, and troubleshooting metadata-related issues.}
      \resumeItem{Troubleshooting}
        {Worked on troubleshooting production issues, environment monitoring, and performance of multiple networks.}
    \resumeItemListEnd

  \resumeSubheading
    {Xiaomi India Technology}{Bangalore, IND}
    {Support Specialist (Operation)}{July 2016 -- January 2017}
    \resumeItemListStart
      \resumeItem{AWS Migration}
        {Worked on Aliyun OS migration to AWS S3 and data migration, implemented and designed a new events-based alerting system using messaging and notification service.}
      \resumeItem{Infrastructure as Code}
        {Implemented Infrastructure as Code and Pipeline as code concepts using CI/CD and infrastructure tools.}
    \resumeItemListEnd

  \resumeSubheading
    {Motif India Infotech}{Ahmedabad, IND}
    {CCR (Operations)}{August 2015 -- July 2016}
    \resumeItemListStart
      \resumeItem{Support Solution}
        {Dealt with buying and general requests from eBay India members, forwarded complaints and requests to various departments within eBay, and handled on-call troubleshooting.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

% Skills/Tools
\section{Skills/Tools}
\resumeSubHeadingListStart
  \resumeSubItem{Programming Skills}
    {Python, Shell, PowerShell, Golang}
  \resumeSubItem{Technical Skills}
    {Jenkins, Terraform, AWS, Azure, GCP(Firebase/Google Analytics and GKE), Ansible, Chef, Linux, Cloud Security, Hashicorp Sentinel, Tenable, Kubernetes (AKS, EKS, GKE), Database (Postgres, Mongodb, MySQL), Monitoring(Prometheus, Grafana, Loki).}
\resumeSubHeadingListEnd

% Certifications
\section{Certifications}
\resumeSubHeadingListStart
  \resumeSubItem{AWS Certified Solutions Architect – Associate}
    {Amazon Web Services (AWS)}
  \resumeSubItem{HashiCorp Certified: Vault Associate (002)}
    {HashiCorp}
  \resumeSubItem{Jenkins - Fundamentals}
    {CloudBees, Inc. }
  \resumeSubItem{Microsoft Certified: Azure Fundamentals AZ-900}
    {Microsoft}
  \resumeSubItem{HashiCorp Certified: Terraform Associate}
    {HashiCorp}
  \resumeSubItem{Microsoft Certified: Azure Security Engineer AZ-500}
    {Microsoft}
  \resumeSubItem{ISO/IEC 27001 Information Security Associate™}
    {SkillFront}
\resumeSubHeadingListEnd

% Footer
\vfill
\textit{* Last updated: \today}

\end{document}
